Note on coherent state

### 2020-03-18 notes/coherent state.tex
3.18完成。主要修改论文前半部分的表述，以及写相干态的note

    \begin{itemize}
        \item Basic propertities for creation and annilation operators.
        \item Coherent states under Hamiltonian representation.
        \item Coherent states under coordinate representation.
        \item Wigner functions for coherent states and time evolution.
        \item classical propertities of coherent states.
    \end{itemize}

    \section{Properties for operators}
        In this section, I'd like to briefly review some basic properties of some operators. The Hamiltonian is $\hat{H}=\frac{\hat{p}^2}{2m}+\frac{1}{2}m\omega^2\hat{x}^2$, and the commute relations is $[\hat{x},\hat{p}]=i\hbar$(Be careful of the sign!). Then the creation and annilation operator can be defined as

@@

        \begin{equation}
            \hat{x}= ,\ \hat{p}= ,\ \hat{H}=(\hat{a}^+\hat{a}+\frac{1}{2})\hbar\omega
        \end{equation}

        Suppose the eigenstate of the Hamiltonian is $\ket{n}$ with eigenvalue $E_n=(n+\frac{1}{2})\hbar\omega$ whose wavefunction is $\Psi_n(x)=$. Then

        \begin{equation}
            \hat{a}\ket{n}=\sqrt{n}\ket{n-1},\ \hat{a}^\dagger\ket{n}=\sqrt{n+1}\ket{n+1}
        \end{equation}

@@

        \begin{equation}
            \hat{a} (\hat{D}(\alpha)\ket{0}) = \alpha (\hat{D}(\alpha)\ket{0})
        \end{equation}

        Therefore, we may define the coherent states as $\ket{\alpha} = \hat{D}(\alpha)\ket{0}$ with ANY complex number eigenvalue $\alpha\in\mathbb{C}$

@@

    \section{Coherent states under Hamiltonian representation}

    \section{Coherent states under coordinate representation}
\end{document}

>>>>

    \begin{itemize}
        \item Basic propertities for creation and annihilation operators.
        \item Coherent states under Hamiltonian representation.
        \item Coherent states under coordinate representation.
        \item Wigner functions for coherent states and time evolution.
        \item classical propertities of coherent states.
    \end{itemize}

    \section{Basic knowledges on oscillators}
        In this section, I'd like to briefly review some basic properties of some operators. The Hamiltonian is $\hat{H}=\frac{\hat{p}^2}{2m}+\frac{1}{2}m\omega^2\hat{x}^2$, and the commute relations is $[\hat{x},\hat{p}]=i\hbar$(Be careful of the sign!). Then the creation and annihilation operator can be defined as

@@

        \begin{equation}
            \begin{split}
                \hat{x}&= \sqrt{\frac{\hbar}{2m\omega}}(\hat{a}^\dagger+\hat{a}) \\
                \hat{p}&= i\sqrt{\frac{m\hbar\omega}{2}}(\hat{a}^\dagger-\hat{a}) \\
                \hat{H}&= (\hat{a}^+\hat{a}+\frac{1}{2})\hbar\omega
            \end{split}
        \end{equation}

        Suppose the eigenstate of the Hamiltonian is $\ket{n}$ with eigenvalue $E_n=(n+\frac{1}{2})\hbar\omega$ whose wavefunction is

        \begin{equation}
            \Psi_n(x)=\bigl(\frac{m\omega}{\pi\hbar}\bigr)^{\frac{1}{4}}\frac{1}{\sqrt{2^n n!}}H_n(\frac{m\omega}{\hbar}x)\exp\bigl(-\frac{m\omega}{2\hbar}x^2\bigr)
        \end{equation}

        Then the creation and annihilation operators give out

        \begin{equation}
            \begin{split}
                \hat{a}\ket{n}&=\sqrt{n}\ket{n-1} \\
                \hat{a}^\dagger\ket{n}&=\sqrt{n+1}\ket{n+1}
            \end{split}
        \end{equation}

        \section{Important opertor formulas}

@@

        \begin{equation}
            \hat{a} \bigl(\hat{D}(\alpha)\ket{0}\bigr) = \alpha \bigl(\hat{D}(\alpha)\ket{0}\bigr)
        \end{equation}

        Therefore, we may define the coherent states as $\ket{\alpha} = \hat{D}(\alpha)\ket{0}$ with ANY complex number eigenvalue $\alpha\in\mathbb{C}$, and $\hat{a}\ket{\alpha}=\alpha\ket{\alpha}$.

        Since $\hat{a}^\dagger$ and $\hat{a}$ can be described by $\hat{x}$ and $\hat{p}$, we can write the translation operator as another form:

        \begin{equation}\label{Weyl translation 1}
            \hat{D}(\alpha) = \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}\hat{x}-i\Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}}\hat{p}\biggr)
        \end{equation}

        It's not difficult to find that $\hat{D}(\alpha)$ is actually a Weyl translation operator $\hat{W}(\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}, \Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}})$. Based on Glauber's formula, we can express $\hat{D}(\alpha)$ as a separated form:

        \begin{equation}\label{Weyl translation 2}
            \hat{D}(\alpha) = \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\alpha}{\hbar}}\hat{x}\biggr) \exp\biggl(-i\Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}}\hat{p}\biggr) \exp(-i \Im(\alpha)\Re(\alpha))
        \end{equation}

@@

    \section{Coherent states under Hamiltonian and coordinate representation}

        Now let's calculate the coherent state under coordinate representation, i.e. wavefunction of the coherent state $\braket{x|\alpha}$. Notice the expression (\ref{Weyl translation 1}) of $\hat{D}(\alpha)$ by $\hat{x}$ and $\hat{p}$, we can consider the operation of $\hat{D}(\alpha)$ over coordinate eigenstate $\ket{x}$. Then  $\braket{x|\alpha}$ can be expressed as $\bra{x}\hat{D}(\alpha)\ket{{0}}$, where the translation operator operates on $\bra{x}$. Note that $\hat{D}(\alpha)^\dagger=\hat{D}(-\alpha)$

        \begin{equation}
            \begin{split}    
                \hat{D}(\alpha)\ket{x} &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\alpha}{\hbar}}\hat{x}\biggr) \exp\biggl(-i\Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}}\hat{p}\biggr) \exp(-i \Im(\alpha)\Re(\alpha)) \ket{x} \\
                    &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}\bigl(x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}\bigr)\biggr) \exp(-i \Im(\alpha)\Re(\alpha)) \ket{x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}} 
            \end{split}
        \end{equation}

\end{document}
